---
header-includes:
   - \usepackage{bbm}
   - \usepackage{graphicx}
   - \usepackage{booktabs}
   - \usepackage{fancyhdr}
   - \usepackage{caption}
output:
  pdf_document: default
  html_document:
    df_print: paged
  word_document: default
fontsize: 12pt
numbersections: true
fig_caption: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rmarkdown)
library(knitr)
```

\setlength{\parskip}{0em}
\pagenumbering{arabic}
\pagestyle{fancy}
\fancyhf{}
\rhead{Émile \textsc{Bourban}, Guillaume \textsc{Pillet}}
\lhead{Florent \textsc{Sierro}, Hugo \textsc{Michel}}
\rfoot{Page \thepage}

\begin{center}
\LARGE{\bfseries{Applied Biostatistics - Regression - Ice cream}}
\end{center}

```{r LoadData, echo=FALSE}
# Set the working directory :

setwd("C:\\Users\\Florent\\Documents\\R\\Projet")
# setwd("C:\\Users\\Emile....")
# setwd("C:\\Users\\Hugo....")
# setwd("C:\\Users\\Guilaume......")

# Clear variables
rm(list=ls(all=TRUE))
# Load Data
icecream <- read.csv("icecream.csv")
str(icecream)
```

L'assistant a dit : Explorer le model, en essayé plrs puis choisr celui qu'on pense le meilleur, 
puis après afficher les résultats du modèle chosit et voir par exemple les valeur extremes !

\section{Introduction}
Guillaume

\section{Multiple regression analysis}
\subsection{Pairwise simple correlations}
Florent
Blablbabla

```{r pairwise regression, echo=FALSE, results="hide", fig.cap="\\label{fig:correlations} Pairwise scatter plot for all variables"}
pairs( ~ moisture + protein + ash, data=icecream)

```




\subsection{Model selection}
Emile
\subsubsection{Forward selection} 
Emile
\subsubsection{Backward selection} 
Emile

\subsection{Regression diagnostics}
Hugo

\subsection{Conclusion}
????



```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
