---
header-includes:
   - \usepackage{bbm}
   - \usepackage{graphicx}
   - \usepackage{booktabs}
   - \usepackage{fancyhdr}
   - \usepackage{caption}
   - \usepackage{geometry}
output:
  pdf_document: default
  html_document:
    df_print: paged
  word_document: default
fontsize: 12pt
numbersections: true
fig_caption: yes
geometry: margin=2.5cm
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rmarkdown)
library(knitr)
library(xtable)
```

\setlength{\parskip}{0em}
\pagenumbering{arabic}
\pagestyle{fancy}
\fancyhf{}
\rhead{Émile \textsc{Bourban}, Guillaume \textsc{Pillet}}
\lhead{Florent \textsc{Sierro}, Hugo \textsc{Michel}}
\rfoot{Page \thepage}

\begin{center}
\LARGE{\bfseries{Give your work a meaningful title (not "Logistic regression")
I should be able to tell what your project is about without reading past the title.
Une idéé qqun ??}}
\end{center}

```{r LoadData, echo=FALSE}
# Set the working directory :

 setwd("C:\\Users\\Florent\\Documents\\R\\Projet")
# setwd("C:\\Users\\Emile....")
# setwd("C:\\Users\\Hugo....")
# setwd("C:\\Users\\gpill\\Documents\\GitHub\\Biostats")

# Clear variables
rm(list=ls(all=TRUE))
# Load Data
icecream <- read.csv("icecream.csv")
str(icecream)
```

L'assistant a dit : Explorer le model, en essayé plrs puis choisr celui qu'on pense le meilleur, 
puis après afficher les résultats du modèle chosit et voir par exemple les valeur extremes !

\section{Introduction}
Manufacturing ice cream cones requies baking of a blatter before rolling it into specifical conic shapes. This batter is compoosed of many ingredients (flour, sugar, water ..) and its quality is a crucial point that was studied by V.T. Huang, J.B. Lindamood and P.M.T. Hansen in a paper they published in 1988. The stake of this study was to optimize the automatization of the manufacturing. Indeed, different problems may emerge from too thin (sticking problem) or too thick (uniformity problem) batter.  
To prevent this situation, they evaluated the quality of the baffer used to prepare the cones depending on several factors. The factor we studied is the viscosity of the flour, influenced by its content in moisture, protein and ash. We developed a model to clarify the relationship between these elements  

\section{Multiple regression analysis}
\subsection{Pairwise simple correlations}
Florent
Blablbabla

```{r pairwise regression, echo=FALSE, results="hide", fig.cap="\\label{fig:correlations} Pairwise scatter plot for all variables"}
pairs( ~ moisture + protein + ash, data=icecream)
```

```{r covariances and correlations, echo=FALSE, results="hide"}
cov(icecream[c(2,3,4)])
cor(icecream[c(2,3,4)])

covariances <- round(cov(icecream[c(2,3,4)]))
correlations <- round(cor(icecream[c(2,3,4)]))

# covtable <- kable(xtable(covariances), format = "latex", booktabs = TRUE)
# cortable <- kable(xtable(correlations),format = "latex", booktabs = TRUE


```




\subsection{Model selection}
Emile
\subsubsection{Forward selection} 
Emile
\subsubsection{Backward selection} 
Emile

\subsection{Regression diagnostics}
Hugo

\subsection{Conclusion}
????



```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
